Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-10-12 paper/paper.tex
more minor changes from R1

First, our model encompasses a broad range of extended playing techniques, well beyond the so-called ``ordinary'' mode of acoustic production.
Specifically, we fit pairwise judgments for 78 different techniques arising from 16 instruments, some of which include removable timbre-altering devices such as mutes.

@@

Timbre involves multiple time scales in conjunction, from a few microseconds for an attack transient to several seconds for a sustained tone.
Therefore, computational models of timbre perception must summarize acoustic information over a long analysis window, typically amounting to $10^{4}$ digital audio samples or more \cite{joder2009taslp}.
Mapping this input to a feature space in which distances denote timbral dissimilarity requires a data-driven stage of dimensionality reduction.
In this respect, the scientific literature exhibits a methodological divide as regards the collection of human-annotated data \cite{siedenburg2016jnmr}: while the field of MIR mostly encodes timbre under the form of ``audio tags'', music psychology mostly measures timbre similarity directly from pairwise similarity judgments.

>>>>

First, our dataset encompasses a broad range of extended playing techniques, well beyond the so-called ``ordinary'' mode of acoustic production.
Specifically, we fit pairwise judgments for 78 different techniques arising from 16 instruments, some of which include removable timbre-altering devices such as mutes.

@@

Timbre involves multiple time scales in conjunction, from a few microseconds for an attack transient to several seconds for a sustained tone.
Therefore, computational models of timbre perception must summarize acoustic information over a long analysis window \cite{joder2009taslp}.
Mapping this input to a feature space in which distances denote timbral dissimilarity requires a data-driven stage of dimensionality reduction.
In this respect, the scientific literature exhibits a methodological divide as regards the collection of human-annotated data \cite{siedenburg2016jnmr}: while the field of MIR mostly encodes timbre under the form of ``audio tags'', music psychology mostly measures timbre similarity directly from pairwise similarity judgments.
